---
title: "machine_learning"
author: "Amit Sanghi"
date: "Sunday, May 24, 2015"
output: html_document
---

The goal of your project is to predict the manner in which they did the exercise. This is the "classe" variable in the training set. You may use any of the other variables to predict with. You should create a report describing how you
built your model, how you used cross validation, what you think the expected out of sample error is, and why you
made the choices you did. You will also use your prediction model to predict 20 different test cases.

```{r}
library(caret)
library(kernlab)
library(C50)
training<-read.table.url("https://d396qusza40orc.cloudfront.net/predmachlearn/pmltraining.csv",skip=4,header=T)
testing<-read.table.url("https://d396qusza40orc.cloudfront.net/predmachlearn/pmltesting.csv",skip=4,header=T)

```
Cleaning the training and testing data set

```{r, echo=FALSE}
## Remove columns with all NA values
training<-training[,!(colSums(is.na(training))>nrow(training)*0.95)]
colnames(training)
## Drop colums which are not relevant for prediction. These are timestamp values or constant values.
training$user_name<- NULL
training$X<- NULL
training$raw_timestamp_part_1<- NULL
training$raw_timestamp_part_2<- NULL
training$cvtd_timestamp<- NULL
training$new_window<- NULL
training$num_window<- NULL
```

Training the model for prediction.

```{r, echo=FALSE}
### 
modelfit<-train(classe~.,data=training,method="glm")
modelfit
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

```{r, echo=FALSE}
### Preoaring testing data set for prediction
testing<-testing[,colnames(testing)%in%colnames(training)] 
```
Predict the results using predict
```{r, echo=FALSE}
### Preparing testing data set for prediction
predictions<-predict(modelfit,newdata = testing)
predictions
```

```{r, echo=FALSE}
### Create folds and cross validate
folds<-createFolds(y=training$classe,k=10,list=TRUE,returnTrain = TRUE)
modelfir_folds<-sapply(folds,train(classe~.,data=training,method="glm"))
sapply(modelfir_folds,predict(modelfir_folds,newdata = testing))
```
